GDPR: Is non-compliance profitable for Meta Platforms, Inc.?

### 2023-06-11 docs/research/LaTeX/research.tex
Finish paper

\begin{abstract}
    % TODO
\end{abstract}

@@

In summary, the fines imposed on \textit{Meta Platforms, Inc.} under the GDPR
have not had a substantial impact on the company's financial performance.
Investor confidence remains intact, as evidenced by the stability of the stock
price and trading volume around the time of the fines. Furthermore, the
company's revenue and net income have not been adversely affected by these
penalties. The only noticeable change is the less volatile average revenue per
person in Europe compared to the US. Especially in the period from 31-Mar-2022
to 31-Dec-2022 where a \%6.45 increase in revenue in the US was met with a
\%10.77 decline in revenue in Europe.

>>>>

\begin{abstract}
    This paper investigates the financial implications of General Data
    Protection Regulation (GDPR) fines on \textit{Meta Platforms, Inc.}
    (formerly \textit{Facebook, Inc.}). By examining net income, revenue, stock
    price, volume of shares traded, and average revenue per person, the study
    assesses the relationship between GDPR penalties and Meta's financial
    performance. The findings suggest that GDPR fines did not have any impact,
    with investor confidence remaining stable, revenue unaffected, and net
    income declining in line with other tech companies. However, a slight
    decline in average revenue per person in Europe compared to the US is
    observed. Further research is needed to explore legal expenses, reputation,
    and user perception related to GDPR non-compliance.
\end{abstract}

@@

In conclusion, the fines imposed on \textit{Meta Platforms, Inc.} under the GDPR
have not had a substantial impact on the company's financial performance.
Investor confidence remains intact, as evidenced by the stability of the stock
price and trading volume around the time of the fines. Furthermore, the
company's revenue and net income have not been adversely affected by these
penalties. The only noticeable change is the less volatile average revenue per
person in Europe compared to the US. Especially in the period from 31-Mar-2022
to 31-Dec-2022 where a \%6.45 increase in revenue in the US was met with a
\%10.77 decline in revenue in Europe.
